Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-02-23 paper/paper1/ms.tex
Refining the introduction

Addressing these and other challenges forms the backbone of spectral calibration, an increasingly valuable specialty as the deficits in our models become intolerable with greater data quantity and quality.  Luckily, many scientific applications in astrophysics do not need the technically demanding noise-free template, nor catalog-of-all-spectral-lines.  A few lines suffice.  For those applications, human inspection of isolated lines and semi-automated equivalent width determination has been and will remain adequate.

But many new and important questions in the fields of stars and exoplanets aspire to reach the margins of what the data can inform.  For example, exoplanet cross-correlation spectroscopy \citep{2013MNRAS.436L..35B} hinges on accurate molecular spectral templates to detect and characterize the atmospheres of exoplanets.  Imperfections in these templates can mute the perceived signal strength of these atmospheric features \citep{2015A&A...575A..20H}.  
In extreme precision radial velocity (EPRV) applications, addressing telluric absorption at the $\mathrm{cm/s}$ level may require joint modeling of the star and the Earth's atmospheric absorption before convolution with an instrumental kernel\footnote{\url{https://speakerdeck.com/dwhgg/telluric-line-hack-week-wrap-up}}.  
In the case of Doppler imaging, an accurate underlying template is needed to detect longitudinally symmetric structures such as polar spots \citep{1983PASP...95..565V, roettenbacher16} or zonal bands \citep{Crossfield14,2021ApJ...906...64A}.  The \texttt{blas\'e} framework is suitable for these and many other applications for which an accurate \emph{evaluable} noise-free template is desired, or for which the properties of a large number of individual spectral lines is sought.

>>>>

Addressing these and other challenges forms the backbone of \emph{spectral calibration}, an increasingly valuable specialty as the deficits in our models become intolerable with greater data quantity and quality.  Luckily, many scientific applications in astrophysics do not need the technically demanding noise-free template, nor catalog-of-all-spectral-lines.  A few lines suffice.  For those applications, human inspection of isolated lines and semi-automated equivalent width determination have been and will remain adequate.

But many new and important questions in the fields of stars and exoplanets aspire to reach the margins of what the entire dataset can inform.  In particular, data from \emph{high-grasp} \'echelle spectrographs possess simultaneously high spectral resolving power and high bandwidth, yielding tens of thousands or possibly millions of independent spectral data points for each star, substar, or exoplanet.  Those applications that seek to gain signal by ``stacking'' or cross-correlating spectral lines can hypothetically gain huge boosts in the accessible signal-to-noise ratio compared to a single or few lines.  Most manual and semi-automated methods cannot take advantage of the entire spectral bandwidth, and may fail to achieve the hypothetical promise of these high-bandwidth spectrographs.

For example, exoplanet cross-correlation spectroscopy \citep{2013MNRAS.436L..35B} hinges on accurate molecular spectral templates to detect and characterize the atmospheres of exoplanets.  Imperfections in these templates can mute the perceived signal strength of these atmospheric features \citep{2015A&A...575A..20H}.  
In extreme precision radial velocity (EPRV) applications, cross-correlation methods work, but addressing telluric absorption at the $\mathrm{cm/s}$ level may require joint modeling of the star and the Earth's atmospheric absorption before convolution with an instrumental kernel\footnote{\url{https://speakerdeck.com/dwhgg/telluric-line-hack-week-wrap-up}}.  
In the case of Doppler imaging, an accurate underlying template is needed to detect longitudinally symmetric structures such as polar spots \citep{1983PASP...95..565V, roettenbacher16} or zonal bands \citep{Crossfield14,2021ApJ...906...64A}.  The \texttt{blas\'e} framework was developed as an enabling technology for these and many other applications for which an accurate \emph{evaluable} noise-free template is desired, or for which the properties of a large number of individual spectral lines is sought.
